\cvsection{Experience}
\begin{cventries}
\experienceentry
    {\textbf{Digital Application Layer}(Senior Associate,Tech)}
    {Rogers Communications, Quest Comm.,Contracting for Sapient}
    {Bangalore, India}
    {Oct. 2018 - May. 2019}
    {\textbf{DAL}, a streaming application used by Rogers' to consume  }
    {Roles:}
    {
      \begin{cvitems}
        \item {Modules to consume kafka trail files:}
\begin{itemize}
\item Developed modules for consuming kafka records, transforming and writing to cassandra with help of scala-alpakka-kafka connectors.
\end{itemize}
\begin{itemize}
\item 
\end{itemize}
\begin{itemize}
\item 
\end{itemize}
        \item {Developed kafka producers for publishing messages so as to assess application's functionality.}
             \end{cvitems}
    }
\experienceentry
    {\textbf{Digital Platform Transformation}(Senior Associate,Tech)}
    {}
    {Bangalore, India}
    {Jan. 2018 - Sept. 2018}
    {\textbf{Rogers.com}, a dashboard portal used by Rogers' customers to view their account/subscription details, update  }
    {Roles:}
    {
      \begin{cvitems}
        \item {APIs to support customers in accessing subscription details:}
\begin{itemize}
\item Developed REST APIs based on Play/Guice framework tied with Akka toolkit to leverage OVO APIs.
\end{itemize}
\begin{itemize}
\item Migrated existing identity management modules to use JWT encrypted tokens
\end{itemize}
\begin{itemize}
\item Helped in deploying the micro-services in akka clusters so as to minimize the transaction overhead. 
\end{itemize}
        \item {Migrated archaic jar dependencies to make them compatible with contemporary versions of \textbf{SBT}.}
             \end{cvitems}
    }
  \experienceentry
    {\textbf{One view optimization}(Senior Associate,Tech)}
    {Rogers Communications, Sapient}
    {Bangalore, India}
    {Oct. 2017 - Dec. 2017}
    {\textbf{One view}, a dashboard portal for Rogers.com. representatives,was being used to interface with customers to help them with previous incidents and interactions,promotional offers. }
    {Roles:}
    {
      \begin{cvitems}
        \item {APIs to support representatives interface:}
\begin{itemize}
\item Developed REST APIs based on Play/Guice framework tied with Akka toolkit.
\end{itemize}
\begin{itemize}
\item Migrated existing APIs so that they can interface with micro-services built on akka-http.
\end{itemize}
\begin{itemize}
\item Helped deployed the micro-services in akka clusters so as to minimize the transaction overhead. 
\end{itemize}
        \item {Migrated archaic jar dependencies to make them compatible with contemporary versions of \textbf{SBT}.}
             \end{cvitems}
    }
    \experienceentry
    {\textbf{Fido High-Speed Internet}(I.T Analyst)}
    {Rogers Communications, TCS}
    {Chennai, India}
    {Nov. 2016 - Mar. 2017}
    {Fido.ca, a sister company of Rogers.com. acted as a consumer sales channel for wireless services, handsets, and broadband modems. \textbf{F}ido \textbf{H}igh-\textbf{S}peed \textbf{I}nternet would let customers buy Internet modems as a standalone product instead of as a bundle of \textbf{H}igh \textbf{S}peed \textbf{I}nternet and \textbf{I}nternet \textbf{P}rotocol \textbf{T}ele\textbf{V}ision. }
    {Roles:}
    {
      \begin{cvitems}
        \item {APIs to support user interface to buy/change \textbf{H}igh \textbf{S}peed-\textbf{I}nternet modems:}
\begin{itemize}
\item Developed REST APIs based on Play/Spring framework tied with Akka toolkit.
\end{itemize}
\begin{itemize}
\item Programmed APIs so that they can interface with SOAP web services and Cassandra DB for user state persistence.
\end{itemize}
\begin{itemize}
\item Integrated remotely deployed Akka modules with native modules to achieve distribution. 
\end{itemize}
        \item {Designed a module to capture error logs in Cassandra database while incorporating Akka streams.}
             \end{cvitems}
    }
 \experienceentry
    {\textbf{Eclipse Minimum Viable Product (MVP) 3.0}(team member)}
    {}
    {Chennai, India}
    {Jan. 2016 - Oct. 2016}
    {Eclipse 3.0 project was Rogers.com', essentially a wireless service provider, foray into catering cable services like \textbf{H}igh\textbf{-}\textbf{S}peed \textbf{I}nternet and \textbf{I}nternet \textbf{P}rotocol \textbf{T}ele\textbf{V}ision as a bundle. This project leveraged API implementations which offered IPTV products to Fido Customers and let them add/remove/swap TV packages, channels, and theme packs. The Fido Eclipse 2.0 experience was made “Rogers like” with Copy and Messaging updates to reflect the Rogers target market (Families) and added necessary new features specific to the Rogers offering to the overall experience to ensure the best customer experience and enjoyment.
}
    {Roles:}
    {
      \begin{cvitems}
        \item {Modularization:}
        \begin{itemize}
\item Molded existing Fido Play/Akka REST APIs into re-usable module jars to be used as \textbf{SBT} dependencies.
\end{itemize}
\begin{itemize}
\item Created REST APIs to exploit module dependencies which could let the user perform payment operations, modify an existing HSI package, add channels/theme packs to an existing TV package or schedule an appointment to install equipment.
\end{itemize}
\begin{itemize}
\item Integrated remotely deployed Akka modules with native modules to achieve distribution. 
\end{itemize}
        \item {Channel search functionality:}
        \begin{itemize}
\item Programmed caching of channel search results from a product catalog to enable swift searching.
\end{itemize}
\begin{itemize}
\item Reconfigured search APIs to handle faceted searching where multiple parameters can be input to filter out the returns.  
\end{itemize}
             \end{cvitems}
    }
     
 
    \experienceentry
    {\textbf{Fido User Migration and Registration}(team member)}
    {}
    {Chennai, India}
    {Apr. 2015 - Jan. 2016}
    {Fido user migration project was launched to migrate legacy customers to a new third party identity management program, enable them to perform social login(or native email based or service Id profile login) and Self-Service (including create a profile, modify a profile, change the forgotten password;)}
    {Roles:}
    {
      \begin{cvitems}
        \item {Web service invoked by Rogers owned sales channels to migrate legacy customers and create a new email based login so that customer can access his details:}
\begin{itemize}
\item Developed and migrated legacy code to an \textbf{Apache CXF}-based web service to be used by third party retailers.
\end{itemize}
\begin{itemize}
\item Programmed Akka based service implementations to go with the WSDL and leverage SOAP web services(and 3rd party identity providers) for user state persistence.
\end{itemize}
        \item {Native APIs to support customer self-service:}
        \begin{itemize}
\item Leveraged third party identity provider's REST services in the native APIs for allowing customer to perform profile update or re-activation of a newly created profile.
\end{itemize}
\begin{itemize}
\item Assisted in programming an API to let a customer search his profile with his email Id.
\end{itemize}
             \end{cvitems}
    }
    \experienceentry
    {\textbf{Fido Eclipse 2.0}(team member)}
    {}
    {Chennai, India}
    {Oct. 2014 - Nov. 2015}
    {Fido Eclipse project introduced APIs to maintain product bundle which included \textbf{H}igh-\textbf{S}peed \textbf{I}nternet and \textbf{I}nternet \textbf{P}rotocol \textbf{T}ele\textbf{V}ision targeted towards millennials. Users were able to check in their consumption(monthly or daily) and schedule installation appointment with the HSI and add/remove channels or theme packs with the IPTV product. It also let legacy customers access/maintain their essential details(home address, payment details and order history). 
}
    {Roles:}
    {
      \begin{cvitems}
        \item {APIs to support user interface which let Fido customers carry out operations like make payment, access usage details, update profile details;}
\begin{itemize}
\item Developed REST APIs based on Play/Spring framework tied with Akka toolkit.
\end{itemize}
\begin{itemize}
\item Programmed APIs so that they can interface with SOAP web services and Cassandra DB for user state persistence.
\end{itemize}
\begin{itemize}
\item Integrated remotely deployed Akka modules with native modules to achieve distribution. 
\end{itemize}
      \end{cvitems} 
    }

    \experienceentry
    {\textbf{SalesCentral}(team member)}
    {}
    {Chennai, India}
    {Mar. 2013 – Apr. 2014}
    {Sales Central, a Web-based Sales Channel, was used by the third party dealers/retailers to place and activate Rogers Wireless, Rogers Cable and Fido Wireless services. Dealers can create a new connection, Exchange/upgrade an existing handset and add/modify plan or add-ons with the help of web interface. }
    {Roles:}
    {\begin{cvitems}
        \item {Revamped services to generate order confirmation PDFs for relevant flows. }
        \item {Developed STRUTS controllers to handle action calls from JSP and AJAX helpers to engage JSF AJAX calls.}
        \item {Remodeled JSP UI pages to JSF/MyFaces pages to enhance user experience and handle user data persistence.}
      \end{cvitems}
    }
\end{cventries}
